Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-06 ms.tex
started cleaning out the PCA section where much of the first principal component variance was bias.

\subsubsection{PCA Correction}
Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
Here, we assume that each column is a random variable that is correlated with the rest of the columns.
Each row represents a different noise iteration.
We first mask all bad pixels by setting all pixels with $| f | > 200$ DN.
The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).
These first 10 principal components explain 10\% of the total variance in each group up the ramp.
The principal components from one group to another are very similar.
\textcolor{red}{\bf Is this just because they contain information from residuals after bias subtraction? Maybe we need a better bias subtraction?}
Indeed, an extra bias subtraction somewhat changes the character and repeatability of the first few principal components shown in Figure \ref{fig:pcaEigenvectorsExtraBias}.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp54.pdf}
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp55.pdf}
\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
}\label{fig:pcaEigenvectors}
\end{figure*}

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_54.pdf}
\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_55.pdf}
\caption{The first 5 principal component eigenvectors identified from group 54 (left) and group 55 (right) where each amplifier has been analyzed independently.
Again, the eigenvectors are very similar other than vertical flips.
}\label{fig:pcaEigenvectors}
\end{figure*}

@@

The characteristic timescale for persistence is 12 seconds, as shown in Figure \ref{fig:persistence}.
Thus, charge trapping release becomes undetectable after 5 minutes and is well below 0.1 DN/s per pixel.
This release time is considerably faster than for Hubble Space Telescope, where the fast-trap release timescale is $e^{5.4}=220$ and the slow-release timescale is $e^{10.1}=24,000$ \citep{zhou2017chargeTrap}.

>>>>

\subsubsection{PCA Correction}
Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
Here, we assume that the counts for each pixel along a column is a random variable that can be correlated with pixels in other columns.
Each row represents a different noise iteration.
First, we calculate the mean value of each pixel in the 108 group stack and subtract all groups by this mean image.
This removes all bias levels and focuses on the time variability of the pixels.
Here, we assume the dark current is negligible.
Next, we mask all bad pixels by setting all pixels with $| f | > 200$ DN to 0 DN to remove bad pixels that can drive the principal components.
The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).

The first 10 principal components explain 14\% of the total variance in each group up the ramp.
The principal components from one group to another are different, but the ordering of these components generally follows a pattern of increasing frequency with higher order principal components.
This is expected for 1/f noise where the lowest frequencies have most of the power.
\textcolor{red}{\bf Is this just because they contain information from residuals after bias subtraction? Maybe we need a better bias subtraction?}
Indeed, an extra bias subtraction somewhat changes the character and repeatability of the first few principal components shown in Figure \ref{fig:pcaEigenvectorsExtraBias}.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_54.pdf}
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_55.pdf}
\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
}\label{fig:pcaEigenvectors}
\end{figure*}

@@

The characteristic timescale for persistence is 12 seconds, as shown in Figure \ref{fig:persistence}.
Thus, charge trapping release becomes undetectable after 5 minutes and is well below 0.1 DN/s per pixel.
This release time is considerably faster than for Hubble Space Telescope, where the fast-trap release timescale is 280 seconds and the slow-release timescale is 16,300 \citep{zhou2017chargeTrap}.
